Approximation as Differentiation: Notes

### 2025-05-19 main/formal-structures.tex

Although it just precomposes with $f$, writing reindexing as $\reindex{-}{f}$ avoids notational confusion when
combining composition of morphisms in $\Func{X}{C}$ with reindexing.

@@

\begin{itemize}
\item $\partial f: \partial X \to T(f)(\partial Y)$;
\item $T(f)(\partial g): T(f)(\partial Y) \to T(f)(T(g)(\partial Z)) = T(g \comp f)(\partial Z)$.
\end{itemize}

>>>>

Although reindexing is just precomposition with $f$, writing it as $\reindex{-}{f}$ avoids notational
confusion when combining composition of morphisms in $\Func{X}{C}$ with reindexing.

@@

\begin{itemize}
\item $\partial f: \partial X \to T(f)(\partial Y)$, and
\item $T(f)(\partial g): T(f)(\partial Y) \to T(f)(T(g)(\partial Z)) = T(g \comp f)(\partial Z)$
\end{itemize}
